\documentclass[fleqn,10pt]{olplainarticle}
% Use option lineno for line numbers 

\title{Critical analysis of Lithium Battery State of Charge Estimation using Memory Mechanisms of Machine Learning}

\author[1]{Mr Marat (Matt) Sadykov}
\author[2]{Dr David Holmes}
\affil[1]{Queensland University of Technology}
%\affil[2]{Address of second author}

\keywords{LSTM, Auto-Regression, SoC}

\begin{abstract}
    \textbf{Implementation of reliable algorithm for determening State of Charge (SoC) of Lithium Ion (Li-Ion) battery in Electrical Vehicle (EV) is one of the major tasks in the Battery Management System (BMS).
    The article proposes a modefied version of a Long Short-Term Memory Recurrent Neural Network (LSTM-RNN) with Auto-regression mechanism.
    The application for this mechanism defined in the feed-forwarding the output of the Machine Learning (ML) model back to itself as an input.
    Initial value of State of Charge becomes another input feature, along with battery Voltage, Current and Temperature.} \\[1pc]
    \textbf{Two dataset were taken from Center for Advanced Life Cycle Engineering (CALCE) for A123 Batteries.
    They consist of Dynamic Stress Test (DST), Supplemential Federal Test Procedure-driving Schedule (US06) and Federal Urban Driving Schedule (FUDS).
    Several combitation of those test on training and validation said acted as cross-validation mechanism as well as time for model to train and number of input samples.} \\[1pc]
    \textbf{LSTM with Auto-Regression achives a root mean squared error of 0.0268 ** ** at early steps of training and improves to ** ** ** with every epoch.
    The final goal is to bring the model to a state at which it can perform an online training on Small On-Chip Computers, by using only recently measured sensor data.}
\end{abstract}

\begin{document}

\flushbottom
\maketitle
\thispagestyle{empty}
%%% Introduction
\input{./I_Introduction/Intro}
%%% Body
\input{./II_Body/feed-forward}
\input{./II_Body/layer}
\input{./II_Body/error}
%%% Conclusion
\input{./III_Conclussion/results}
\input{./III_Conclussion/conclussion}
\input{./III_Conclussion/acknowledgements}

\bibliography{bibs}

\end{document}